Stack Safety is a Security Property

### 2021-04-15 tex/main.tex
More polishing / comments

\caption{Another confidentiality violation}
\label{fig:conf2}
\end{figure}

@@

10 f:     add $1,%sp        ; allocate frame
11        cmp stash, $0     ; compare
12        breq #15          ; branch if equal
13        mov -2(%sp),stash ; update stash
14        jmp #17
15        mov stash,-2(%sp) ; retrieve stash
16        mov $0,stash
17        sub $1,%sp        ; deallocate frame
18        ret
\end{verbatim}
}
  \end{subfigure}
  \begin{subfigure}{.4\textwidth}
    \begin{tabular}{l l l}
      {\tt 3} &
      \memoryaddrs{8em}
      \memory{3}{\unsealc}
      ~$\cdots$
      \MemoryLabel{-15em}{0.75em}{1} \\
      {\tt 18} &
      \memoryaddrs{12em}
      \memory{1}{\mainsealc}[Seal(0)]%
      \memory{1}{\unsealc}[RetPtr]%
      \memory{1}{\unsealc}%
      ~$\cdots$
      \MemoryLabel{-15em}{0.75em}{1}
      \MemoryLabel{-11em}{0.75em}{\#4}
      \vspace{.5em} &
      \memory[3em]{1}{\mainsealc}[Target]%
      \MemoryLabel{-3em}{0.75em}{\(\PCname\) = \#4}
      \\
      {\tt 4} &
      \memoryaddrs{8em}
      \memory{3}{\unsealc}
      ~$\cdots$
      \MemoryLabel{-15em}{0.75em}{1} \\
      {\tt 11} &
      \memoryaddrs{16em}
      \memory{1}{\mainsealc}
      \memory{2}{\unsealc}%
      ~$\cdots$
      \MemoryLabel{-15em}{0.75em}{-1}
      \MemoryLabel{-11em}{0.75em}{\#6} &
      \memory[3em]{1}{\mainsealc}
      \MemoryLabel{-3em}{0.75em}{\(\PCname\) = \#6}
      \\
      {\tt 18} &
      \memoryaddrs{12em}
      \memory{1}{\mainsealc}
      \memory{1}{\badc}
      \memory{1}{\unsealc}%
      ~$\cdots$
      \MemoryLabel{-15em}{0.75em}{-1}
      \MemoryLabel{-11em}{0.75em}{\#4} &
      \memory[3em]{1}{\mainsealc}
      \MemoryLabel{-3em}{0.75em}{\(\PCname\) = \#6}
      \\
      {\tt 4} &
      \memoryaddrs{8em}
      \memory{1}{\mainsealc}
      \memory{2}{\unsealc}
      ~$\cdots$
      \MemoryLabel{-15em}{0.75em}{-1} &
      \memory[3em]{1}{\mainsealc}
      \MemoryLabel{-3em}{0.75em}{\(\PCname\) = \#6}
      \\
      {\tt 5} &
      \memoryaddrs{8em}
      \memory{1}{\mainsealc}
      \memory{2}{\unsealc}
      ~$\cdots$
      \MemoryLabel{-15em}{0.75em}{\bf 1} &
      \memory[3em]{1}{\mainsealc}
      \MemoryLabel{-3em}{0.75em}{\(\PCname\) = \#6} \\
    \end{tabular}
  \end{subfigure}
  \caption{A control-flow attack}
  \label{fig:controlflow}
\end{figure}

@@

We next define our machine model precisely. To make our definition of stack safety
as generic as possible, this section proposes an abstract interface to a
machine model plus some kind of (software- or hardware-enforced) policy monitor.
In~\cref{sec:enforcement}, we instantiate this model with a concrete dynamic
policy enforcement mechanism based on \citet{DBLP:conf/sp/RoesslerD18}.

@@

\caption{Sharing on the stack}
\label{fig:passingsimple}
\end{figure}

>>>>

\caption{Another confidentiality violation \bcp{Again, let's align the C
    code with the assembly, etc.}}
\label{fig:conf2}
\end{figure}

@@

10 f:     add $1,%sp        ; allocate frame
11        cmp stash, $0     ; compare
12        breq #15          ; branch if equal
13        mov -2(%sp),stash ; update stash
14        jmp #17
15        mov stash,-2(%sp) ; retrieve stash
16        mov $0,stash
17        sub $1,%sp        ; deallocate frame
18        ret
\end{verbatim}
}
  \end{subfigure}
  \begin{subfigure}{.4\textwidth}
    \begin{tabular}{l l l}
      {\tt 3} &
      \memoryaddrs{8em}
      \memory{3}{\unsealc}
      ~$\cdots$
      \MemoryLabel{-15em}{0.75em}{1} \\
      {\tt 18} &
      \memoryaddrs{12em}
      \memory{1}{\mainsealc}[Seal(0)]%
      \memory{1}{\unsealc}[RetPtr]%
      \memory{1}{\unsealc}%
      ~$\cdots$
      \MemoryLabel{-15em}{0.75em}{1}
      \MemoryLabel{-11em}{0.75em}{\#4}
      \vspace{.5em} &
      \memory[3em]{1}{\mainsealc}[Target]%
      \MemoryLabel{-3em}{0.75em}{\(\PCname\) = \#4}
      \\
      {\tt 4} &
      \memoryaddrs{8em}
      \memory{3}{\unsealc}
      ~$\cdots$
      \MemoryLabel{-15em}{0.75em}{1} \\
      {\tt 11} &
      \memoryaddrs{16em}
      \memory{1}{\mainsealc}
      \memory{2}{\unsealc}%
      ~$\cdots$
      \MemoryLabel{-15em}{0.75em}{-1}
      \MemoryLabel{-11em}{0.75em}{\#6} &
      \memory[3em]{1}{\mainsealc}
      \MemoryLabel{-3em}{0.75em}{\(\PCname\) = \#6}
      \\
      {\tt 18} &
      \memoryaddrs{12em}
      \memory{1}{\mainsealc}
      \memory{1}{\badc}
      \memory{1}{\unsealc}%
      ~$\cdots$
      \MemoryLabel{-15em}{0.75em}{-1}
      \MemoryLabel{-11em}{0.75em}{\#4} &
      \memory[3em]{1}{\mainsealc}
      \MemoryLabel{-3em}{0.75em}{\(\PCname\) = \#6}
      \\
      {\tt 4} &
      \memoryaddrs{8em}
      \memory{1}{\mainsealc}
      \memory{2}{\unsealc}
      ~$\cdots$
      \MemoryLabel{-15em}{0.75em}{-1} &
      \memory[3em]{1}{\mainsealc}
      \MemoryLabel{-3em}{0.75em}{\(\PCname\) = \#6}
      \\
      {\tt 5} &
      \memoryaddrs{8em}
      \memory{1}{\mainsealc}
      \memory{2}{\unsealc}
      ~$\cdots$
      \MemoryLabel{-15em}{0.75em}{\bf 1} &
      \memory[3em]{1}{\mainsealc}
      \MemoryLabel{-3em}{0.75em}{\(\PCname\) = \#6} \\
    \end{tabular}
  \end{subfigure}
  \caption{A control-flow attack \bcp{wonder if we can cram the bottom part
      onto the same row as the rest.  Might need to make things smaller,
      spill into the margin, etc., but we really need the space.  (Another
      option is to make it a separate figure and flow text around it, but
      this will save less space.)}}
  \label{fig:controlflow}
\end{figure}

@@

We now define our machine model precisely. To make our definition of stack safety
as generic as possible, this section proposes an abstract interface to a
machine model plus some kind of (software- or hardware-enforced) policy monitor.
In~\cref{sec:enforcement}, we instantiate this model with a concrete dynamic
policy enforcement mechanism based on \citet{DBLP:conf/sp/RoesslerD18}.

@@

\caption{Sharing on the stack \ifaftersubmission\bcp{Not enough space above the bottom part of
    the figure (at least in the latex build that I'm looking at...)}\fi}
\label{fig:passingsimple}
\end{figure}
